{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-26 paper/paper.tex
explained intuition of the sequential typing judgment
beautified section about typing

\todo{Explain intuition}
\begin{enumerate}
\item We have a partial ordered set $(\text{LType}, \leq)$ of local types, with an initial
      type $t_{init}$
\item and typing judgments of the form $se, i \vdash_{seq} s \Rightarrow t$, where
      $s, t \in \text{LType}$, $i \in \mathcal{P}$ and se is a securirty environment.
\end{enumerate}

@@

\todo{beautify me}
\begin{figure}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] \in SeqIns \\ se, i \vdash_{seq} s \Rightarrow t}
{se, i \vdash s \Rightarrow t}
\end{align*}
\end{minipage}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] = \mathtt{start} pc \\ se(i) \leq se(pc)}
{se, i \vdash s \Rightarrow s}
\end{align*}
\end{minipage}
\caption{Extension of the sequential typing rules}
\label{fig:multithreaded-typing-rules}
\end{figure}

@@

A program is typeable in this type system $\mathcal{S}, se \vdash P$, where a function $\mathcal{S}:
\mathcal{P} \rightarrow LType$ that maps a local type to every program point
and a security environment $se$, iff $\mathcal{S}$ maps every initial program point
(including the ones of spawned threads) to $t_{init}$ and for every program point $j$ which is an
successor of $i$ there is a type $s \in LType$, such that $s$ is lower bounded
by $\mathcal{S}(j)$ and $se, i \vdash \mathcal{S}(i) \Rightarrow s$ holds.

>>>>

\begin{enumerate}
\item We have a partial ordered set $(\text{LType}, \leq)$ of local types, with an initial
      type $\textsc{t}_{init}$
\item and typing judgments of the form $se, i \vdash_{seq} \textsc{s} \Rightarrow \textsc{t}$, where
      $\textsc{s}, \textsc{t} \in \text{LType}$, $i \in \mathcal{P}$ and se is a securirty environment.
\end{enumerate}

The intuition of the typing judgment is that if we execute the instruction at program
point $i$ w.r.t. the security environment $se$ and the current type is $\textsc{s}$. Then the
type after the execution is $\textsc{t}$.

@@

\begin{figure}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] \in \text{SeqIns} \\ se, i \vdash_{seq} \textsc{s} \Rightarrow \textsc{t}}
{se, i \vdash \textsc{s} \Rightarrow \textsc{t}}
\end{align*}
\end{minipage}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] = \mathtt{start}\ pc \\ se(i) \leq se(pc)}
{se, i \vdash \textsc{s} \Rightarrow \textsc{s}}
\end{align*}
\end{minipage}
\caption{Extension of the sequential typing rules}
\label{fig:multithreaded-typing-rules}
\end{figure}

@@

A program is typeable in this type system $\mathcal{S}, se \vdash P$, where a function $\mathcal{S}:
\mathcal{P} \rightarrow \text{LType}$ that maps a local type to every program point
and a security environment $se$, iff $\mathcal{S}$ maps every initial program point
(including the ones of spawned threads) to $\textsc{t}_{init}$ and for every program point $j$ which is an
successor of $i$ there is a type $s \in \text{LType}$, such that $\textsc{s}$ is lower bounded
by $\mathcal{S}(j)$ and $se, i \vdash \mathcal{S}(i) \Rightarrow \textsc{s}$ holds.
